### 2019-01-11 journal/conclusions.tex
journal start

{\scriptsize {\bf Acknowledgements:} The authors would like to thank the authors of
the MUSEUM \cite{multilingual} and Metallaxis-FL vs. MUSE 
\cite{Papadakis} data sets, who provided both data and prompt assistance with
its analysis.  In particular, Shin Hong and Thierry Chekam were
extremely helpful in use of these data sets.}

>>>>

{\scriptsize {\bf Acknowledgements:} The authors would like to thank the authors of
the MUSEUM \cite{multilingual} and Metallaxis-FL vs. MUSE 
\cite{Papadakis} studies for access to their data sets.  In
particular, we thank Shin Hong and Thierry Chekam for prompt
assistance beyond the call of duty.}

### 2019-01-11 journal/experiments.tex
journal start

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best benchmark curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve (first 15 tests) is worse compared to the benchmark curve, but still has a maximum gap of only 2 redundant tests vs. 4 for the benchmark.  Over all, again the curve is better than the best benchmark curve at 60\% of all points.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

For GCC wrong code faults, the baseline chance that two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric showed the same fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity (\% of repaired tests corresponding to most common repaired fault) was 79.4\%, median 100\%.

>>>>

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best benchmark curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve (first 15 tests) is worse compared to the benchmark curve, but still has a maximum gap of only 2 redundant tests vs. 4 for the benchmark.  Over all, again the curve is better than the best benchmark curve at 60\% of all points.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage will see 20 faults after 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

For GCC wrong code faults, the baseline chance that two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric showed the same fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity was 79.4\% (median 100\%).

### 2019-01-11 journal/metrics.tex
journal start

For every failing test case, its response to mutants defines a bit-vector, with
length equal to the number of mutants that repaired any test case,
where a 1 bit indicates that the mutant in question repairs this test
case\footnote{By \emph{repairing} a failing test we mean that a mutant
causes the test to pass, and the mutant does not cause
other, previously passing tests, to fail.}.  These cannot be effectively compared with Hamming distance. Consider $t_1$ and $t_2$, both repaired
by 100 mutants.  If these two test cases share 90 common repairing
mutants, and disagree for 10, they have a Hamming
distance of 20.  This makes them ``less similar'' than two test cases,
$t_1'$ and $t_2'$, where $t_1'$ is repaired by 5 mutants, $t_2'$ is
repaired by 5 mutants, and \emph{none of those mutants overlap.}   A Jaccard distance, also used (as similarity) in some fault
localization algorithms \cite{Pinpoint}, is a better fit.  For bitvectors $u$ and $v$ of length $n$:
%\vspace{-0.08in}
\[d(u,v) = 
\begin{cases}
\frac{\sum_{i=0}^{n-1} 1\ \text{if}\ u_i \neq v_i\ \text{else}\ 0}{\sum_{i=0}^{n-1} 1
\  \text{if}\ u_i \neq 0 \vee v_i \neq 0\ \text{else}\ 0} & \exists i:u_i\neq 0 \vee v_i\neq 0\\
0 & otherwise
\end{cases}
\]

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons\footnote{In Section \ref{conc} we discuss uses of $d$
requiring comparison of both failing and passing test cases:  in this 
case, we would use three-valued vectors, where 1 indicates a 
failing property succeeds and -1 that a succeeding property 
fails.}.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.

@@

>>>>

For every failing test case, its response to mutants defines a bit-vector, with
length equal to the number of mutants that repaired any test case,
where a 1 bit indicates that the mutant in question repairs this test
case\footnote{By \emph{repairing} a failing test we here mean that a mutant
causes the test to pass, \emph{and} the mutant does not cause
other, previously passing tests, to fail.}.  These cannot be effectively compared with Hamming distance. Consider $t_1$ and $t_2$, both repaired
by 100 mutants.  If these two test cases share 90 common repairing
mutants, and disagree for 10, they have a Hamming
distance of 20.  This makes them ``less similar'' than two test cases,
$t_1'$ and $t_2'$, where $t_1'$ is repaired by 5 mutants, $t_2'$ is
repaired by 5 mutants, and \emph{none of those mutants overlap.}   A Jaccard distance, also used (as similarity) in some fault
localization algorithms \cite{Pinpoint}, is a better fit.  For bitvectors $u$ and $v$ of length $n$:
%\vspace{-0.08in}
\[d(u,v) = 
\begin{cases}
\frac{\sum_{i=0}^{n-1} 1\ \text{if}\ u_i \neq v_i\ \text{else}\ 0}{\sum_{i=0}^{n-1} 1
\  \text{if}\ u_i \neq 0 \vee v_i \neq 0\ \text{else}\ 0} & \exists i:u_i\neq 0 \vee v_i\neq 0\\
0 & otherwise
\end{cases}
\]

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.
\comment{
\footnote{In Section \ref{conc} we discuss uses of $d$
requiring comparison of both failing and passing test cases:  in this 
case, we would use three-valued vectors, where 1 indicates a 
failing property succeeds and -1 that a succeeding property 
fails.  For such an application, we could remove the requirement that
a repair not be a killed mutant, since the passing test vectors would encode
that information.}}

@@

In Section \ref{conc} we discuss uses of $d$
requiring comparison of both failing and passing test cases:  in this 
case, we would use three-valued vectors, with a bit for each \emph{property}, where 1 indicates a 
failing property succeeds and -1 that a succeeding property 
fails.  For such an application, we could remove the requirement that
a repair not be a killed mutant, since the passing test vectors would encode
that information

### 2019-01-11 journal/oldintro.tex
journal start

The proposed techniques in this paper are motivated in large part by progress in automated testing.  Recent advances, some implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in modern optimizing compilers.  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
This paper proposes the use of mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. \comment{The approach suggests a plausible metric for comparing any two program executions, not just failing test cases.  Comparing executions has been a prominent concept in dynamic analysis throughout much of the last two decades \cite{NearNeighbor,Sumner2011} (e.g., Ball's early discussion of profile similarity \cite{BallConcept}).}

\subsection{Fuzzer Taming and Debugging Assistance}

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13,OneTest}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one test's fault; then re-run all tests, until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 5/8/2017, clang had 107 unresolved, assigned bugs, some dating to 2008 \cite{clangbugs}.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing long-standing problems is unlikely.    Applying a novel fuzzing technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, and high priority faults may be hidden by stubborn low-priority faults.

Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  Their proposed solution was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.

Fuzzer taming results using FPF were promising, but limited.  Rather than proposing a universal metric for use in fuzzer taming, Chen et al. offered many possible metrics (based on ideas in the literature, such as edit distances \cite{lev} or coverage spectra \cite{RepsSpectra} methods), none of which performed notably well across all three of their benchmark data sets, and some of which were not even applicable to all data sets.  For the two most difficult benchmarks, none of the metrics performed extremely well. FPF-based approaches remain in need of a universal but effective metric, particularly for the critical first 50 test cases examined \cite{PLDI13}.

One reason fuzzer taming is needed is that debugging compiler faults is, as noted, difficult.  If developers were able to fix faults quickly once they were identified, it would not be as important to have very good fault identification.  Many duplicate failures could be removed by fixing the underlying faults.  Ideally, a technique able to provide effective fuzzer taming should be able to translate its underlying rationale into some form of automated debugging assistance.   A variety of automated debugging methods \cite{NearNeighbor,GroceError} have been based on distance, so there is reason to expect that a high-quality metric might also contribute to fault localization.

\subsection{Comparison by Response to Mutation}

The methods we propose are based on an idea with numerous possible applications: \emph{if two test cases that fail can be made to succeed by the same small modification to the original program $P$, this provides evidence that they fail due to the same fault}.  The idea is hardly controversial:  most developers determine if they have fixed all faults in a set of failing test cases by re-running the tests after they fix at least one fault.  As a method for fuzzer taming or debugging assistance, however, this is useless.  Fortunately, developer-provided patches are not the only source of changes to a program.  Mutation analysis \cite{demillo1978hints,budd1980theoretical} applies large numbers of small syntactic changes to a program, usually to evaluate a test suite \cite{mutant,justmutants}.  Some recent work has also considered these changes as a source of fixes or localizations for program faults \cite{achour,multilingual,MUSE,DebroyMutant}.  Published empirical data \cite{GopinathMutants}, as well as our data, suggests that very few compiler faults are due to the kind of simple syntactic changes found in mutants.  However, what should matter is that failures, which correspond to faults, can be made to succeed.  When a test case $t$ fails for program $P$ but succeeds for mutant $m$ of $P$ we say that $m$ \emph{repairs} $t$ (in practice, we will usually restrict this to unkilled mutants $m$).  In most cases this does not mean that $m$ is the inverse of a fault, but that $m$ somehow avoids the consequence of a fault.  It is not important that repairs actually fix anything, if all we seek is a way to decide whether failures are due to the same fault.

This idea is in fact a consequence of a more general (and difficult to investigate) hypothesis.  What is interesting about a program execution?  For many purposes, the only interesting properties of an execution are those that in some way relate to the correctness properties of the program, assuming we have a good set of correctness properties.  These may include assertions, differential testing \cite{Differential,ICSEDiff}, timing constraints, temporal logic formulas, or any other checkable properties.  What, then, makes two executions similar?  Our proposal is that \emph{two executions of $P$ are similar to the degree that changes to $P$ produce the same changes in correctness of the executions.}

This leads to the general idea of comparing any two executions by their response to mutants, since a mutant can cause a passing or failing test to violate more/different properties.   However, for practical purposes the most interesting implication is that if two failing test cases can be made to differ as to whether they fail by a mutant, this provides evidence that they fail due to different faults.

\comment{
%Where there are multiple, independent, correctness properties, this even allows us to compare failing and successful executions, since a mutant can cause a failure to violate a different property.
{\bf Hypothesis 2} at first may suggest that this idea subsumes past notions of similarity, such as spectra of code coverage, since if two executions do not cover a statement, they both cannot alter correctness if that statement is altered.  The metrics are in fact simply incomparable:  for example, differences in coverage that never have an effect on correctness cannot contribute to similarity in our approach; with weak correctness properties most executions are very similar.  This is similar to the idea of \emph{checked coverage}:  code that cannot impact correctness is not interesting \cite{CheckCov}.  Hypothesis 2 also suggests an additional hypothesis related to hypothesis 1.  This is {\bf Hypothesis 1a:} If two failing test cases can be made to differ as to whether they fail by a modification of $P$, this provides evidence that they fail due to different faults.
}

%\subsection{The Onion-Ring and Causality}

This not a claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is presumably \emph{some} level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Must we then characterize mutant granularity?  No.

\begin{figure}
\centering
\includegraphics[width=0.4\columnwidth]{onionring}
\caption{\scriptsize{Onion-ring shows all repairs for the center-most test case, and all other test cases repaired by same mutants.  Rings represent repairing mutants, and diamonds test cases.  Diamond pattern symbolizes fault.  For innermost ring, all failures are due to the same fault.  As rings expand, the set of faults grows (as does distance).}}
\vspace{-0.1in}
\label{fig:onion}
\end{figure}

Consider the structure of mutants repairing a failure due to some optimization.  If many mutants repair this failure, by turning off the optimization or a whole family of optimizations, some will likely repair failures due to different faults.  Repairs naturally produce an \emph{onion-ring} structure (Figure \ref{fig:onion}), where a failure is repaired by (1) some mutants that are very specific to its fault (the inner rings) and repair few failures, as well as other mutants (2) that repair more and more faults, up to a hypothetical mutant (3) that turns off all optimization in the compiler (e.g., by effectively adding {\tt -O0}), the outer ring of the onion.  This does not introduce confusion, because the more repairs two tests have in common, the more likely they are to be due to the same fault, and the more they disagree on, the less likely they are to be due to the same fault.  While especially intuitive as a consequence of disabling compiler optimizations, it seems likely this structure appears for repairs in many programs.  Disabling an optimization is a code change that (usually) does not cause any test case that only concerns semantics, not speed, to fail, but can avoid some failures.  For some oracles, many changes may fall into this classification:  for example, if the only oracle is to detect crashes, a fault can be avoided by aborting the program early.  Turning off a data-structure invariant checker is another possible false repair that might cover many different faults.  In all these cases, assuming more interesting and specific ways to repair faults exist, a distance metric can still work.

The idea of measuring the distance between failures (or other test cases) by their response to mutants is appealing.  The most important aspect of most applications of distances between executions is some aspect of causality \cite{LewisCause,ZellerBook}.  Since at least the work of Hume \cite{Hume1}, causality has been understood as answering some question of the form ``what would have made a difference in this effect?''  A program mutant is a very direct way to answer this question.  The problem with determining causes of events in computer programs is that, as in most problems of causality, too many things can make a difference, most of which are not interesting.  Program mutants are much more likely to be interesting causes for events in a program than changes to test cases, at least for fault identification and debugging purposes, because the practical use of knowing a cause is to change the cause and avoid or produce an effect.  Debugging by changing test cases is not useful; debugging by altering the program is precisely how we seek to use the causes we discover.  Using mutants as causes in order to measure similarity ``inverts'' the ideas of Lewis \cite{LewisCause,LewisCount}, where similarity determines causality.  One pleasant side-effect is that execution representation \cite{NearNeighbor,RepsSpectra} is not a difficulty for this kind of metric, since an execution is always represented as a set of correctness evaluations.

This paper investigates the utility of using distance metrics based on the causal approach suggested above.  We show that such a metric can improve, in a statistically significant way, the ability to distinguish tests based on which faults they trigger.  Furthermore, fault localization based on the same metrics can successfully pinpoint the location of some compiler faults sufficiently to be likely to substantially aid debugging, and, when applicable, performs very well for some faults studied in recent papers on mutant-based fault localization \cite{multilingual,Papadakis}.

%\subsection{Contributions}

The contributions of this paper include our ideas about how to measure distance between program executions, but more importantly some practical proposals for using such a metric in compiler fuzzer taming and fault localization.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over best previous results \cite{PLDI13}, in multiple ways.  Our fault localization approach also compares favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual,Metallaxis}, albeit with a more limited applicability (but also a lower cost).

>>>>

Recent advances in automated test generation, reported in numerous papers and implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in, e.g., modern optimizing compilers\footnote{In this paper, we take the problem of testing and debugging compilers as representative of the general problem of testing and debugging complex critical systems software.}.  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of program mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. The approach suggests a pThese may include assertions, differential testing \cite{Differential,ICSEDiff}, timing constraints, temporal logic formulas, or any other checkable properties.  What, then, makes two executions similar?  Our proposal is to say that:

\begin{quote}
{\bf Hypothesis 2:} Two executions of $P$ are similar to the degree that changes to $P$ produce the same changes in correctness of the executions.
\end{quote}

This leads to the idea of comparing executions by their response to mutants.   In the presence of multiple correctness properties, any two executions can be compared, not just two failures, since a mutant can cause a failure to violate additional or different properties.
%Where there are multiple, independent, correctness properties, this even allows us to compare failing and successful executions, since a mutant can cause a failure to violate a different property.
{\bf Hypothesis 2} at first may suggest that this idea subsumes past notions of similarity, such as spectra of code coverage, since if two executions do not cover a statement, they both cannot alter correctness if that statement is altered.  The metrics are in fact simply incomparable:  for example, differences in coverage that never have an effect on correctness cannot contribute to similarity in our approach; with weak correctness properties most executions are very similar.  This is similar to the idea of \emph{checked coverage}:  code that cannot impact correctness is not interesting \cite{CheckCov}.  Hypothesis 2 also suggests an additional hypothesis related to hypothesis 1.  This is {\bf Hypothesis 1a:} If two failing test cases can be made to differ as to whether they fail by a modification of $P$, this provides evidence that they fail due to different faults.

\subsection{The Onion-Ring and Causality}

These hypothesis do not claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is certainly some level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Characterizing the granularity of program mutants is likely difficult, but fortunately it is not necessary.

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{onionring}
\caption{\scriptsize{The onion-ring model of repairs, showing all repairs for the center-most test case, and all other test cases repaired by those mutants.  Circles represent repairing mutants, and diamonds repaired test cases.  Diamond pattern symbolizes fault.  For the innermost ring of repairing mutant(s), all test cases are due to the same fault.  As rings expand to include more failures, the set of faults repaired grows (as does distance).}}
\label{fig:onion}
\end{figure}

Consider the structure of mutants repairing a failure due to some optimization.  If many mutants repair this failure, by turning off the optimization or a whole family of optimizations, some will likely repair failures due to different faults.  Repairs naturally produce an \emph{onion-ring} structure (Figure \ref{fig:onion}), where a failure is repaired by (1) some mutants that are very specific to its fault (the inner rings) and repair few failures, as well as other mutants (2) that repair more and more faults, up to a hypothetical mutant (3) that turns off all optimization in the compiler (e.g., by effectively adding {\tt -O0}), the outer ring of the onion.  This does not introduce confusion, because the more repairs two tests have in common, the more likely they are to be due to the same fault, and the more they disagree on, the less likely they are to be due to the same fault.  While especially intuitive as a consequence of disabling compiler optimizations, it seems likely this structure appears for repairs in many programs.  Disabling an optimization is a code change that (usually) does not cause any test case that only concerns semantics, not speed, to fail, but can avoid some failures.  For some oracles, many changes may fall into this classification:  for example, if the only oracle is to detect crashes, a fault can be avoided by aborting the program early.  Turning off a data-structure invariant checker is another possible false repair that might cover many different faults.  In all these cases, so long as there are other, more interesting and more specific ways to repair some faults, a distance metric can still distinguish faults effectively.

The idea of measuring the distance between failures (or other test cases) by their response to mutants is appealing.  The most important aspect of most applications of distances between executions is some aspect of causality \cite{LewisCause,ZellerBook}.  Since at least the work of Hume \cite{Hume1}, causality has been understood as answering some question of the form ``what would have made a difference in this effect?''  A program mutant is a very direct way to answer this question.  The problem with determining causes of events in computer programs is that, as in most problems of causality, too many things can make a difference, most of which are not interesting.  Program mutants are much more likely to be interesting causes for events in a program than changes to test cases, at least for fault identification and debugging purposes, because the practical use of knowing a cause is to change the cause and avoid or produce an effect.  Debugging by changing test cases is not useful; debugging by altering the program is precisely how we seek to use the causes we discover.  Using mutants as causes in order to measure similarity essentially inverts the ideas of David Lewis \cite{LewisCause,LewisCount}, where similarity is used to determine causality.

\subsection{Contributions}

The contributions of this paper are: hypotheses about how to measure distance between program executions, and practical proposals for using such a metric in fuzzer taming and in novel fault localization and explanation methods.  Evaluating the effectiveness of these methods also provides experimental evidence as to the validity of our hypotheses.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over previous results \cite{PLDI13}, in multiple ways.  Our preliminary localization approaches compare favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual}, for the mutation analysis budget in our experiments.

### 2019-01-11 journal/othertools.tex
journal start

The {\bf Repair} localization was designed for use in compiler (or at least complex system software) fuzzing.  It is not proposed (or at least, not here evaluated) as a general-purpose fault localization method.  However, it is possible to compare {\bf Repair} with other methods, using their full mutation and experimental set, to provide a more apples-to-apples comparison than the evaluation vs. MUSE and MUSEUM over compiler faults.  We obtained the data from two evaluations of mutant-based fault localization methods:  the set of faults used to evaluate MUSEUM \cite{multilingual}, and a set of CoREBench \cite{CoREBench} faults used in an evaluation of MUSE and Metallaxis-FL by Chekal et. al \cite{Papadakis} (we were unable to obtain the original MUSE dataset, thus far).  These data sets are not ideal for evaluating {\bf Repair}: for all but 10 of the faults (all from the CoREBench set) there is only a single failing test case in the data.  {\bf Repair} for single failing tests is essentially MUSEUM without use of passing tests, except to reject any mutation that breaks a passing test.  {\bf Repair} is meant to operate in the case where a program either has numerous failing tests associated with open bugs (e.g., a typical production compiler or complex system software program) or where a program has just been fuzzed for the first time, so has numerous failures representing different faults.  The distance metric lets {\bf Repair} make use of these other faults, by enabling it to focus on repairing mutants most relevant to the failing test.

>>>>

The {\bf Repair} localization was designed for use in compiler (or at least complex system software) fuzzing.  It is not proposed (or at least, not here evaluated) as a general-purpose fault localization method.  However, it is possible to compare {\bf Repair} with other methods, using their full mutation and experimental set, to provide a more generalizable (and fair) comparison than the evaluation vs. MUSE and MUSEUM over compiler faults.  We obtained the data from two evaluations of mutant-based fault localization methods:  the set of faults used to evaluate MUSEUM \cite{multilingual}, and a set of CoREBench \cite{CoREBench} faults used in an evaluation of MUSE and Metallaxis-FL by Chekal et. al \cite{Papadakis} (we were unable to obtain the original MUSE dataset, thus far).  These data sets are not ideal for evaluating {\bf Repair}: for all but 10 of the faults (all from the CoREBench set) there is only a single failing test case in the data.  {\bf Repair} for single failing tests is essentially MUSEUM without use of passing tests, except to reject any mutation that breaks a passing test.  {\bf Repair} is meant to operate in the case where a program either has numerous failing tests associated with open bugs (e.g., a typical production compiler or complex system software program) or where a program has just been fuzzed for the first time, so has numerous failures representing different faults.  The distance metric lets {\bf Repair} make use of these other faults, by enabling it to focus on repairing mutants most relevant to the failing test.  {\bf Repair} can, in many cases, have a lower cost than MUSEUM or Metallaxis-FL because it does not need to run mutants that do not repair any failing tests on the passing tests: analysis can begin with failing tests and only analyze passing tests covering repairing mutants.
